\documentclass[12pt]{article}
\usepackage[top=1.25in, bottom=1.25in, left=1in, right=1in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}

\setlength\parindent{0cm}
\setitemize{itemsep=-2pt}
\titleformat{\section}{\normalfont\Large\bfseries}{\thesection}{1em}{}[{\titlerule[0.8pt]}]


\begin{document}

\moveleft.5\hoffset\centerline{\Large\bf Benjamin E. Noland}
\smallskip
\moveleft.5\hoffset\centerline{291 Moore Street}
\moveleft.5\hoffset\centerline{Princeton, NJ, 08540}
\moveleft.5\hoffset\centerline{609-851-1137}
\moveleft.5\hoffset\centerline{benjaminnoland93@gmail.com}
%\moveleft.5\hoffset\centerline{benjamin.noland@rutgers.edu}
\moveleft.5\hoffset\centerline{http://bnoland.github.io/}

\section*{Education}

\textbf{Rutgers University}, New Brunswick, NJ, September 2012-May 2016 \\
BA in mathematics, minor in physics \\
School of Arts and Sciences Honors Program \\
GPA: 3.525

\subsection*{Relevant coursework:}
\begin{itemize}
\item
\textbf{Mathematics:} Calculus, linear algebra, ordinary differential equations, real analysis, complex variables, differential geometry, linear programming, abstract algebra, topology \textit{(taken at Rutgers University)}

\item
\textbf{Physics:}
Classical mechanics, electromagnetism, astrophysics \textit{(taken at Rutgers University)}

\item
\textbf{Computer science:}
Systems programming, data structures and algorithms \textit{(taken at Princeton University while in high school)}
\end{itemize}

\section*{Computer Skills}
\begin{itemize}
\item
\textbf{Proficient with:} C, Java, Python, R, \LaTeX, Windows, Unix, Git, Microsoft Office (and similar tools)
\item
\textbf{Experience with:} Stata, JavaScript (including JQuery), HTML, CSS, PHP, MySQL, x86 assembly language
\item
\textbf{GitHub account:} github.com/bnoland
\end{itemize}

\section*{Experience}

\textit{\textbf{Programming intern}} \\
\textbf{Vertices, LLC}, New Brunswick, NJ, May 2015-August 2015
\begin{itemize}
\item
Worked on Mappler, an online geographic information system (GIS) tool. Designed and implemented a feature that allows users to upload images, extracts GPS data from the images, and adds them to the map database.
\item
Partially implemented a daemon for extracting images and associated GPS data from email accounts and adding them to a map database.
\end{itemize}

\textit{\textbf{Programming intern}} \\
\textbf{Voorhees Transportation Center}, New Brunswick, NJ, July 2014-August 2014
\begin{itemize}
\item
Designed and implemented a website that maps crashes involving vehicles and pedestrians (including bicyclists) using data provided by the New Jersey Department of Transportation.
\item
The site allows the user to submit search queries to filter the data. The site can be found at:

\centering{http://pppolicy.rutgers.edu/vtcdata/pedestrian/pedmap.html}
\end{itemize}

\section*{Additional Experience}

\textit{\textbf{Tutoring (informal)}} \\
\textbf{Rutgers University}, New Brunswick, NJ, September 2012-May 2016
\begin{itemize}
\item
Provided informal tutoring in programming and mathematics to students at Rutgers University.
\end{itemize}

\textit{\textbf{Head of Computer Club}} \\
\textbf{Princeton High School}, Princeton, NJ, September 2009-February 2012
\begin{itemize}
\item
Worked with club members towards developing a robot that could navigate a maze.
\item
Organized fundraising for the club.
\item
Taught other students the basics of programming.
\end{itemize}

\textit{\textbf{Video game development program}} \\
\textbf{Rensselaer Polytechnic Institute}, Troy, NY, July 2011
\begin{itemize}
\item
Learned the basics of video game development.
\item
Developed a small game in a team environment using Python and Pygame.
\end{itemize}

\textit{\textbf{Taught robotics to elementary school students}} \\
\textbf{Riverside Elementary School}, Princeton, NJ, January 2011-March 2011
\begin{itemize}
\item
Used Lego to teach the elements of robotics to elementary school students.
\end{itemize}

\section*{Honors}
\begin{itemize}
\item
\textbf{2014 Rutgers Academic Excellence Award}, April 2014
\item
\textbf{Princeton High School Computer Science Award}, June 2012
\end{itemize}

\end{document}
